### 2022-06-15 sections/summary.tex
Update summary.tex

My research is funded by the Chilean National Agency for Research and Development and the St Hilda’s College Muriel Wise Fund.
\vspace{1mm}
\end{cvparagraph}

>>>>

My research is funded by the Chilean National Agency for Research and Development, the St Hilda’s College Muriel Wise Fund and the Society for Latin American Studies Postgraduate and Postdoctoral Research Award.
\vspace{1mm}
\end{cvparagraph}
